Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 PandaEvolution.tex
Notes clean-up

\mtnote{Address Alexei's comments: Add a paragraph explaining how this solution
has been ported to other HPC machines and reference relevant publications.}
While PanDA Broker implementation is resource specific, it was successfully
ported also to other supercomputers, including the Ansel (?) at \ldots and
\ldots at the National Energy Research Scientific Computing Center (NERSC).

>>>>

\mtnote{Address Alexei's comments: Add a paragraph explaining how this solution
has been ported to other HPC machines and reference relevant publications.}
While PanDA Broker implementation is resource specific, it was successfully
ported also to other supercomputers, including the Ansel (?) at \ldots and
Cori at the National Energy Research Scientific Computing Center (NERSC).

### 2017-04-04 bckground.tex
Notes clean-up

\jhanote{(ii) real comparison should be to the Gliden-in WMS ecosystem and use
this as opportunity to narrate the reasons for the divergence.}\mtnote{From our
meetings with Sergey: Before Run 1, ATLAS management become uncomfortable with
the pace at which other WMS were being developed, loosing trust in their ability
to deliver production-grade capabilities. ATLAS USA decided to go solo and
developed their own solution. PanDA proven to be able to deliver the
usual pilot-based WMS capabilities at the right scale. For that, it was chosen
over other solutions.}

>>>>

% \jhanote{(ii) real comparison should be to the Gliden-in WMS ecosystem and use
% this as opportunity to narrate the reasons for the divergence.}\mtnote{From our
% meetings with Sergey: Before Run 1, ATLAS management become uncomfortable with
% the pace at which other WMS were being developed, loosing trust in their ability
% to deliver production-grade capabilities. ATLAS USA decided to go solo and
% developed their own solution. PanDA proven to be able to deliver the
% usual pilot-based WMS capabilities at the right scale. For that, it was chosen
% over other solutions.}
